The Galactic Delay-Time Distribution of Type Ia Supernovae:\\ A Chemical Evolution Perspective

### 2023-07-10 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{deluxetable*}{lll}
\tablecaption{Summary of SN Ia DTD models explored in this paper.}
\tablehead{
\colhead{Model} & \colhead{Parameters} & \colhead{Similar to}
}
\startdata
Power-law   & $\alpha=-1.1$     & \citet[][field]{Maoz2017-CosmicDTD}; 
                                  \citet{Wiseman2021-DESRates}              \\
            & $\alpha=-1.4$     & \citet[][cluster]{Maoz2017-CosmicDTD}; 
                                  \citet{Heringer2019-FieldGalaxyDTD}       \\
Exponential & $\tau=1.5$ Gyr    & \citet[][SD]{Greggio2005-AnalyticalRates};
                                  \citet{Schonrich2009-RadialMixing,
                                         Weinberg2017-ChemicalEquilibrium}  \\
            & $\tau=3.0$ Gyr    & \\
Plateau     & $W=0.3$ Gyr, $\alpha=-1.1$    & \citet[][CLOSE DD]{Greggio2005-AnalyticalRates} \\
            & $W=1.0$ Gyr, $\alpha=-1.1$    & \citet[][WIDE DD]{Greggio2005-AnalyticalRates} \\
Prompt      & $t_{\rm max}=0.05$ Gyr, $\sigma=0.015$ Gyr, $\tau=3.0$ Gyr & \citet{Mannucci2006-TwoPopulations} \\
Triple      & & \citet{Rajamuthukumar2022-TripleEvolution}
\enddata
\end{deluxetable*}

>>>>

\begin{deluxetable*}{lll}
\tablecaption{Summary of SN Ia DTD models explored in this paper.}
\tablehead{
\colhead{Model} & \colhead{Parameters} & \colhead{Similar to}
}
\startdata
Power-law   & $\alpha=-1.1$     & \citet[][field]{Maoz2017-CosmicDTD}; 
                                  \citet{Wiseman2021-DESRates}              \\
Power-law   & $\alpha=-1.4$     & \citet[][cluster]{Maoz2017-CosmicDTD}; 
                                  \citet{Heringer2019-FieldGalaxyDTD}       \\
Exponential & $\tau=1.5$ Gyr    & \citet[][SD]{Greggio2005-AnalyticalRates};
                                  \citet{Schonrich2009-RadialMixing};       \\
            &                   & \citet{Weinberg2017-ChemicalEquilibrium}  \\
Exponential & $\tau=3.0$ Gyr    & \\
Plateau     & $W=0.3$ Gyr, $\alpha=-1.1$    & \citet[][CLOSE DD]{Greggio2005-AnalyticalRates} \\
Plateau     & $W=1.0$ Gyr, $\alpha=-1.1$    & \citet[][WIDE DD]{Greggio2005-AnalyticalRates} \\
Prompt      & $t_{\rm max}=0.05$ Gyr, $\sigma=0.015$ Gyr, & \citet{Mannucci2006-TwoPopulations} \\
            & $\tau=3.0$ Gyr & \\
Triple      & $f_{\rm init}=0.05f_{\rm peak}$, $t_{\rm rise}=0.5$ Gyr, & \citet{Rajamuthukumar2022-TripleEvolution} \\
            & $W=0.5$ Gyr, $\alpha=-1.1$ & \\
\enddata
\end{deluxetable*}
